Bayesian inference of prehistoric demography from multiple proxies: a case study from the Swiss plateau

### 2022-05-23 manuscript/paper.Rmd
Restructure section headings
* Created a background section
* Split materials and methods and gave them more informative titles
* Made case/terminology consistent between headings
Remove old comments

## Evaluation of existing approaches

@@

## Strengths of a hierarchical Bayesian approach

@@

# Materials and Methods

## Background

@@

## Data/Proxies

@@

### Dendro Dated Lakeshore Settlements

@@

### ^14^C sum calibration

@@

### Aoristic Sum

@@

<!-- JR: At the resolution the figure is rendered at, I don't think the 1 km jitter is perceptible. MH: But in the data table that accompanies the repository, they would be available -->

```{r aoristmap, fig.cap="The location of the sites from the find reports of the cantonal archaeology (heritage management). The locations are fuzzified by ~1km."}
my_basemap + geom_point(data = aorist_latlng_coords, aes(x = X, y = Y), color = "black", alpha = 0.75) + blank() + my_scalebar
```

@@

### Openness Indicator

@@

## Process Model

@@

Thus, we can define the limits, the $max\_change\_rate$<!-- JR: no Greek letter? :( MH: I could invent one, if you like? ;-) --> as an time independent variable, again without already specifying them with fixed values at this stage. The estimation of these parameters for the entire model, as well as the estimation of the respective population change per time section, results from the modelling and the interaction with the data, respectively. Overall, this represents a hierarchical model that can be noted as follows:

@@

## Observational Model

@@

<!-- JR: I really like the idea of discussing "dead ends" in the model design process – very modern and reflexive! Maybe hightlight these in a section of their own? MH: I do not feel that this part would provide enough material to justify an own section. -->

@@

<!-- JR: I really think we need a section evaluating and validating the model fit before we discuss its output. MH: that was the intention of the Model fitting section before, but I think this rather belongs to methods than to results!?-->

@@

# Conclusion and Outlook

>>>>

# Background

## Existing approaches to population estimation

@@

## Hierarchical Bayesian demographic models

@@

## Assumptions of a Bayesian approach

@@

# <!-- Materials -->Population proxy data

@@

## Dendro-dated lakeshore settlements

@@

## Summed radiocarbon

@@

## Aoristic sum

@@

```{r aoristmap, fig.cap="The location of the sites from the find reports of the cantonal archaeology (heritage management). The locations are 'fuzzed' by ~1km."}
my_basemap + geom_point(data = aorist_latlng_coords, aes(x = X, y = Y), color = "black", alpha = 0.75) + blank() + my_scalebar
```

@@

## Landscape openness

@@

# <!-- Methods -->Bayesian model

## Process model

@@

Thus, we can define the limits, the $max\_change\_rate$ as an time independent variable, again without already specifying them with fixed values at this stage. The estimation of these parameters for the entire model, as well as the estimation of the respective population change per time section, results from the modelling and the interaction with the data, respectively. Overall, this represents a hierarchical model that can be noted as follows:

@@

## Observational model

@@

@@

@@

# Conclusions
